\clearpage


\section*{\Huge Problem description}
\addcontentsline{toc}{chapter}{Problem description}	
$\\[0.5cm]$
\textbf{Crowdsourced and cloud based mobile application testing} \\
A mobile applications has to be deployed into many different types of mobile devices. The mobile devices can be from different suppliers, and can have very different screen size, memory size, battery capability, and operating systems. The differences of mobile devices are more problematic for Android mobile devices than for Apple ones.\\
The current practices for mobile application testing is to test the mobile application on different simulators. However, if there are many different simulators, run the application tests on all simulators manually or half-manually will be time-consuming.\\
The idea of this project is to consolidate many mobile simulators into one cloud. Tester can simply upload the mobile application on the cloud and run the test on the one simulator of the cloud, the tests will be recorded and be replayed in all other simulators in the cloud automatically.\\
The cloud testing service will be provided for free to all mobile application developers and testers. The could testing service will also support several developers coordinate the testing using crowdsourced testing approaches.\\

The task of the Master thesis will include:
\begin{enumerate}
	\item A short literature review of the crodsrouced and cloud based testing and mobile application testing.
	\item Implementation of the crowdesourced and cloud-based testing service.
	\item Evaluation of the service using a mobile application.
\end{enumerate}


\clearpage